%
% File: abstract.tex
% Author: Your Name
% Description: Contains the text for thesis abstract
%

\chapter*{Abstract}

\begin{center}
    {\HUGE \color{citecolour} The Green Bonds Premium Puzzle \par}
    \vspace{2.5mm}
    {\Large \textit{Evidence from Causal Machine Learning}}
    \vspace{6.5mm}
    
    {\centering\large\textsc{Arbian Halilaj}}
    \vspace{6.5mm}
\end{center}


%\begin{SingleSpace}
\initial{T}his paper measures the greenium effect by using a novel tool from the causal machine learning literature. By employing the causal forest algorithm, we aim to estimate the average treatment effect (ATE) as well as the conditional average treatment effect (CATE) of a bond labelled as green in the primary market. Our data universe comes from the Eikon Refinitiv database, from which we have derived three distinct data samples. We employ three different estimation strategies, including an ensemble method with propensity score matching, resulting in a total of 11 models. Overall, our results show that the greenium effect ranges from 18.6 to 103.2 basis points, with a central tendency of 43 basis points. This effect is statistically and economically significant. We further show that violating the i.i.d assumption has a small negative effect on the estimation accuracy of the average treatment effect of causal forests.
%\end{SingleSpace}

\vspace{14mm}

{\textbf{JEL Classification}} 
A13; G12; Q01; Q51; Q56.

{\large \textbf{\textsc{Keywords:}}} {\textsc{Sustainable Finance; Green Bonds; Greenium; Primary Market; Causal Inference; Causal Machine Learning; Causal Forest.}}


\clearpage